\chapter*{概要}
\addcontentsline{toc}{chapter}{概要}

\par
Conventional single rotor helicopters with $N$ blades generally experience 1/rev and N /rev vibration.
Regarding $N$/rev vibration, for the case of $N=4$, it was confirmed from the analysis using
CAMRAD $\mathrm{II}$ (Comprehensive Analytical Model of Rotorcraft Aerodynamics and Dynamics),
that it is possible to alleviate high angle of attack, which a blade experiences in the azimuthal region
on the retreating side by changing the trim, and it is possible to do so by changing the CG position toward leftward and also rearward,
when a main rotor rotates in a CW direction.
Flight tests have been conducted for a 4 bladed radio-controlled helicopter with a rotor diameter of about 1.5 m
with its CG position varied.
The test results are what were expected to be and show that the vibration can be reduced.
Furthermore, it was demonstrated that differences in hub configuration due to
the presence or absence of a lead-lag hinge affect flap motion and inertial forces, reducing the 4/rev component of the hub vertical load.
From the above, it has been demonstrated that the 4/rev vibration of a single-rotor helicopter can be effectively
reduced by optimizing the CG shift and hub configuration.
This research outcome brings pilot fatigue reduction, reduces the failure rate of equipment of helicopters, and can improve
accuracy of atmospheric observation using helicopters. 
The optimal design of CG displacement, considering trade-offs with attitude changes during takeoff and landing, remains a future challenge.